---
title: "Project 1"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Project 1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(DSA5041Project)
```


# myConstructor
This function takes in two vectors of varying lengths and a significance level and performs a 2 sample t.test. It ouputs a dataframe of the two vectors, the significance level, the confidence interval from the test.
```{r}
myConstructor <- function(x, y, alpha) {

  # Perform two-sample t-test assuming equal variances
  ttest_result <- t.test(x, y, var.equal = TRUE)

  # Calculate confidence interval
  conf_int <- ttest_result$conf.int

  # Calculate p-value
  p_value <- ttest_result$p.value

  # Create a data frame containing x and y
  max_length <- max(length(x), length(y))
  df <- data.frame("X" = rep(NA, max_length), "Y" = rep(NA, max_length))
  df[1:length(x), "X"] <- x
  df[1:length(y), "Y"] <- y

  # Create a named list with the data frame, alpha, confidence interval, and p-value
  result <- list(
    data = df,
    alpha = alpha,
    conf_int = conf_int,
    p_value = p_value
  )

  # Set the class of the list to "Rttest"
  class(result) <- "Rttest"

  return(result)
}
```


# print.Rttest

This function is a method of the generic function "print()." When print is called on an Rttest class object, this method will output the dataframe, alpha, confidence interval, and p-value.
```{r}
print.Rttest <- function(x, ...) {
  cat("\nData Frame:\n")
  print(kableExtra::kable(x$data, format = 'simple'))
  cat("\nAlpha: ", x$alpha, "\n")
  cat("\nConfidence Interval for mu_x - mu_y: [", x$conf_int[1], ", ", x$conf_int[2], "]\n")
  cat("\nP-value: ", x$p_value, "\n")
}
```




```{r}
set.seed(21);x <-rnorm(30,5,2); set.seed(23); y<- rnorm(30, 3,2); alpha <- 0.05
obj <- myConstructor(x=x,y=y,alpha = 0.05)
class(obj)
```


``` {r}
print(obj)
```

