---
title: "Project 1"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Project 1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(DSA5041Project)
```


# myConstructor

This function takes in two vectors of varying lengths and a significance level and performs a 2 sample t.test. It ouputs a dataframe of the two vectors, the significance level, the confidence interval from the test.

```{r}
set.seed(21);x <-rnorm(30,5,2); set.seed(23); y<- rnorm(30, 3,2); alpha <- 0.05
obj <- myConstructor(x=x,y=y,alpha = 0.05)
class(obj)
```

# print.Rttest

This function is a method of the generic function "print()." When print is called on an Rttest class object, this method will output the dataframe, alpha, confidence interval, and p-value.

``` {r}
print(obj)
```

# plot.Rttest

This function is a method of the generic function "plot()." When it is supplied with an Rttest class object, it returns a side-by-side boxplot of the variables in the object.

```{r}
plot(obj)
```

